Reply to Reviewer #1

### 2022-02-15 Writing/CEA_2nd_round/replies_rev_1.rmd
Edit the formatting for re-submission to CEA

First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$. In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures. <span style = "color: blue;"> Shun put table and figure numbers here </span>.

@@

<span style="color:blue">  
Shun is running simulations on training dataset and will report the results.
</span>

>>>>

First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$. In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1.1, Figure C.1.1).

@@

<span style="color:blue">  
We have newly added the results of training accuracy to Appendix D. 
</span>
